---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# shinyGeoRSS


This is a [Shiny](https://shiny.rstudio.com) App for mapping geoRSS feeds, using the [tidyRSS](https://github.com/RobertMyles/tidyRSS) package, along with [leaflet](https://rstudio.github.io/leaflet/), [shinyMaterial](https://ericrayanderson.github.io/shinymaterial/), [DT](https://shiny.rstudio.com/articles/datatables.html) and Shiny & htmltools.  

I made this to show the potential of parsing geoRSS feeds using tidyRSS, since these feeds naturally lend themselves to mapping, and with their streaming-like quality, could make excellent data inputs for a variety of apps.



## Usage

To see the app, just install the package:  

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("RobertMyles/shinyGeoRSS")
```

...and then use the function `runApp()`. It looks better in a browser such as Chrome or Firefox. 